̥---
title: "African American Achievements"
author: "Anirudh Jayaraman"
date: "11/06/2020"
output: html
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading possibly relevant libraries (that we can keep adding to)

```{r}
library(tidyverse)
theme_set(new = theme_light())
```

Getting the data!

```{r}
choose_how <- 1  # Set this to either 0 or 1

if(choose_how == 0){
  # Either read with Github csv urls ------------------------------------------
  firsts_url <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-09/firsts.csv"
  science_url <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-09/science.csv"
  
  firsts <- readr::read_csv(firsts_url)
  science <- readr::read_csv(science_url)
} else {
  # Or read in with tidytuesdayR package --------------------------------------
  # (https://github.com/thebioengineer/tidytuesdayR)
 
  choose_again <- 1  # Set this to either 0 or 1

  if(choose_again == 0){
    tuesdata <- tidytuesdayR::tt_load('2020-06-09')
  } else {
    tuesdata <- tidytuesdayR::tt_load(2020, week = 24)
  }
  
  firsts <- tuesdata$firsts
  science <- tuesdata$science
}
```

```{r}
View(firsts)
View(science)
```

## Firsts

```{r}
firsts %>% 
  ggplot(mapping = aes(x = year, fill = category)) +
  geom_histogram(bins = 50)
```

```{r}
firsts %>% 
  ggplot(mapping = aes(x = year, fill = category)) +
  geom_histogram(bins = 50) + 
  facet_wrap(~ category)
```

```{r}
firsts %>% count(category, sort = TRUE)
```

```{r}

firsts %>%
  count(category, sort = TRUE) %>%
  mutate(category = fct_reorder(category, n)) %>%
  ggplot(mapping = aes(x = n, y = category)) + 
  geom_col()
```

```{r}
firsts %>% select(person)
```

Removing any text from the person column following [ or (
```{r}
firsts %>%
  mutate(person = str_remove(person, pattern = "[\\(\\[].*"),
         person = str_trim(person)) %>%
  select(person)
```

Changing the Firsts dataset to reflect cleaned Person column

```{r}
firsts <- firsts %>%
  mutate(person = str_remove(person, "[\\(\\[].*"),
         person = str_trim(person))

```

```{r}
tuesdata
```

Interactive Graphics

```{r}
library(plotly)
library(glue)
```

Attempting a timeline via plotly

```{r}
g <- firsts %>%
  ggplot(mapping = aes(x = year, 
                       y = category, 
                       color = category,
                       text = glue("{year}, {accomplishment},\n{person}"))) + 
  geom_point() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major.y = element_blank()) + 
  labs(title = "Timeline of some notable African-American achievements", 
       caption = "Source: https://en.wikipedia.org/wiki/List_of_African-American_firsts") 

ggplotly(g, tooltip = "text")
```

## Science

```{r}
science
```

```{r}
science %>%
  count(occupation_s) %>%
  arrange(desc(n)) %>% head(n = 10)
```

Some occupations are list separated by semicolons. The data currently has 120 rows and 7 columns. Let's expand the dataset based on one occupation instance in each row.

```{r}
science %>%
  separate_rows(occupation_s, sep = ";") %>%
  mutate(occupation = str_to_title(occupation_s)) %>%
  count(occupation, sort = TRUE)

science %>%
  separate_rows(occupation_s, sep = ";")
```

Filter the dataset for 'scientists' and 'ians' of any kind
```{r}
science %>%
  separate_rows(occupation_s, sep = ";") %>%
  filter(str_detect(regex(pattern = "scientist", ignore_case = TRUE), 
                    string = occupation_s) | 
           str_detect(string = occupation_s, 
                      pattern = regex(".*ian")))
```

```{r}
science %>% 
  pull(links)
```

```{r}
library(rvest)
```

```{r}
read_html("https://en.wikipedia.org/wiki/David_Blackwell") %>%
  html_node(".vcard") %>%
  as.character
```

```{r}
read_html("https://en.wikipedia.org/wiki/David_Blackwell") %>%
  html_node(".vcard") %>%
  html_table()
```

```{r}
read_html("https://en.wikipedia.org/wiki/David_Blackwell") %>%
  html_node(".vcard") %>%
  html_table() %>%
  set_names("key", "value") %>%
  as_tibble()
```

```{r}
science %>%
  head
```

science_html now has a column named html, containing XML
```{r}
science_html <- science %>%
  separate_rows(occupation_s, sep = ";") %>%
  mutate(html = map(links, possibly(.f = read_html, 
                                    otherwise = NULL, 
                                    quiet = FALSE)))
```

Let's pull the html column (which is a list in reality)
```{r}
science_html %>% pull(html) %>% head
```

Anonymous function

```{r}
extract_infobox <- . %>%
  html_node(".vcard") %>%
  html_table(header = FALSE) %>%
  as.tibble()
```

```{r}
extract_infobox
```

Applying this function to science_html

```{r}
science_html %>% 
  glimpse
```

```{r}
science_html %>%
  mutate(infobox = map(html, possibly(.f = extract_infobox, 
                                   otherwise = NULL, 
                                   quiet = TRUE)))
```

```{r}
science_html %>%
  mutate(infobox = map(html, possibly(.f = extract_infobox, 
                                   otherwise = NULL, 
                                   quiet = TRUE))) %>%
  glimpse
```

```{r}
science_html %>%
  mutate(infobox = map(html, possibly(.f = extract_infobox, 
                                   otherwise = NULL, 
                                   quiet = TRUE))) %>%
  filter(!map_lgl(infobox, is.null))
```